\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[margin=10mm]{geometry}
\raggedbottom
\usepackage{palatino}
\fontfamily{SansSerif}\selectfont
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\definecolor{mygrey}{gray}{0.75}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}


\usepackage{booktabs, makecell, tabularx}
\renewcommand\arraystretch{1.3}
\usepackage{verbatim}
\usepackage{pbox}

\usepackage{enumitem}
\setlist[itemize]{leftmargin=*}

\usepackage{url}

\setlength{\parindent}{0pt}
\pagestyle{empty}
\pdfgentounicode=1
%-----------------------------------------------------------
%Custom commands
\newcommand{\resheading}[1]{\medskip
    \colorbox{mygrey}{\begin{minipage}{\dimexpr\textwidth-2\fboxsep\relax}\small 
                        \textbf{#1 \vphantom{p\^{E}}}
                      \end{minipage}}
                            \par\medskip}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}
    \textsc{\textbf{#1}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------

\begin{document}
\linespread{1.25}

\begin{center} \fontsize{15}{15} \textbf{KHUSHI SAXENA} \end{center}
Roll No.: \textbf{202151078} \\
Mobile No.: \textbf{+91-9837987749} \\
Email-id : \textbf{khushi24saxena@gmail.com} \\
Institute Email-id : \textbf{202151078@iiitvadodara.ac.in} \\
GitHub Profile : \href{https://github.com/khushiisaxena}{https://github.com/khushiisaxena} \\
LinkedIn Profile : \href{https://www.linkedin.com/in/khushi-saxena-a965ba22a/}{https://www.linkedin.com/in/khushi-saxena-a965ba22a} \\


\resheading{\textbf{EDUCATION} }
\begin{tabularx}{\linewidth}{l X l l}
    \midrule
\textbf{Year}
     & \textbf{Degree}  & \textbf{Institute}   & \textbf{CPI/Percentage}   \\
    \midrule
2021 - 2025
     & B.Tech (Computer Science)
                        & Indian Institute of Information Technology, Vadodara            & 7.48 CPI         \\

2020 & 12$^{th}$ CBSE 
                        & Kendriya Vidyalaya NER, Bareilly    & 94.2 \%            \\

2018 & 10$^{th}$ CBSE 
                        & Kendriya Vidyalaya NER, Bareilly    & 95.2 \%           \\
    \midrule
\end{tabularx}

\resheading{\textbf{INTERNSHIPS AND WORK EXPERIENCE}}
\begin{itemize}
    \item \textbf{Quality Assurance Engineer Intern, AMAZON} \hfill \textit{(May 2023 - July 2023, Chennai)}
    \begin{itemize}
        \item Served as a member of the Amazon Payment Services Team
        
        \item Worked on UI Automation of test cases and did manual testing also 


        \item Tools and Technologies Used: Java and Selenium 

    \end{itemize}
\end{itemize}

            

\resheading{PROJECTS}

\begin{itemize}
    \item \textbf{Heart-Failure-Prediction}   \href{https://github.com/khushiisaxena/Heart-Failure-Prediction}{(See Project)}

    \begin{itemize}
        \item  This project aims to improve the accuracy of heart failure prediction models using hyperparameter optimization and feature selection.
        \item 8 supervised learning classification algorithms namely Logistic Regression, KNN, Naive Bayes, SVM, Decision Tree, Random Forest, LightGBM, and XGBoost predictions were analyzed and improved upon using hyperparameter optimization and feature selection.
        \item An accuracy of 87.83\% was achieved using Random Forest for all 12 features and KNN for top 5 features (selected after feature selection).
    \end{itemize}
\end{itemize}

 \begin{itemize}
    \item \textbf{IntelliFace - A Face Recognition-based Attendance System} \href{https://github.com/khushiisaxena/Intelliface}{(See Project)}
    \begin{itemize}
        \item  The system employs a trained CNN for precise facial feature recognition, enhanced by Dlib for landmark detection and NumPy for efficient data manipulation.
        \item Attendance records are stored in CSV files for seamless management.
        \item Real-time image processing, facilitated by OpenCV, enhances the user-friendly solution, revolutionizing attendance tracking in educational and corporate settings.
    \end{itemize}
\end{itemize}

    \begin{itemize}
    \item \textbf{InnVogue- A Hotel Booking Web Application} \href{https://github.com/khushiisaxena/InnVogue.com/tree/master}{(See Project)}
    \begin{itemize}
        \item  Implemented a user-friendly interface for users to search for hotels based on location, dates, and budget.
        \item     Integrated Google Maps API to display the hotel's location and nearby attractions.
    \end{itemize}
\end{itemize}

\resheading{TECHNICAL SKILLS}
    \begin{itemize}
    \item \textbf{Programming: }
    {Java, C, Python, C++}

    \item \textbf{Web Development: }
     {HTML, CSS, JavaScript}

    \item \textbf{Databases: }
     {MySQL, SQLite} 

     \item \textbf{Familiar: }
     {Machine Learning, Deep Learning, Selenium, Git, VS Code, IntelliJIDEA, Jupyter Notebook, Problem Solving}

     \item \textbf{Technical Coursework: }
     {Data Structures and Algorithms (DSA), Database Management Systems (DBMS), Operating Systems (OS), Object Oriented Programming Language (OOPS), Software Engineering (SE), Computer Networks (CN), System Design Analysis, Artificial Intelligence (AI), Cryptography, Data Analytics, Computer Organisation and Architecture, Management Information Systems, Wireless Network Systems}
    
\end{itemize}

\resheading{ACHIEVEMENTS} 
\begin{itemize}
     \item Harvard WECode Scholar 2023: Attended fully funded WIT Global Conference by Harvard University.
     \item Secured 1st position (Girl Category) at CodeStrike (Intra-College Coding Competition). 
    \item Amazon FFE Scholar: Been in the top 49 students, selected for Amazon's Internship, Mentorship, and Training Program.
    \item Selected for Ericsson Empowering Girl Scholarship Program for Engineering Students 2022.
    \item Accomplished the Microsoft Learn - AI Skill Challenge 2024.
    
\end{itemize}

\resheading{RESEARCH} 
\begin{itemize}
    \item Conducted a research study and developed a survey instrument to collect data on the Impact of E-LEARNING On Students And Teachers during COVID-19 and after the pandemic.

\end{itemize}

\resheading{EXTRA-CURRICULAR ACTIVITIES}
    \begin{itemize}
    \item Hobbies: Swimming, Dancing, Photography, Singing
    
\item Secured the second position in the Intra-Institute Sports Fest in badminton.

\item Active member of the Literature Committee, Cultural Committee, Dance Club, Photography Club, and Art Club of IIIT Vadodara.

\item   Participated as a representative of my institute in the Badminton category at the Inter IIIT 2023 sports competition, securing notable achievements.

    \end{itemize}

\end{document}
